The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-08-17 Stickleback_Paper.tex

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.6\linewidth]{matplotlibPlots/MeanPhenotype1.png}
  		\caption{
            Distribution of mean trait values throughout each simulation.
            The dashed pink and purple lines show the optima ($\pm 10$).
		}
  		\label{fig:MeanPhenotype}
	\end{center}
\end{figure}
\plr{Is this the whole simulation? what about the initial adaptation phase?
     Is the horizontal line at the median? what are the whiskers at?}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.8\linewidth]{matplotlibPlots/FST_HRR.png}
  		\caption{
            Distributions of $F_{st}$ values between the three habitats,
            accumulated across the course of the simulation, calculated 
            \textbf{(left)} using only neutral mutations, and
            \textbf{(right)} using effect mutations.
        }
  		\label{fig:Fst}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
        \includegraphics[width=0.8\linewidth]{matplotlibPlots/TimeToAdaptation}
        \caption{
            Time to adaptation as a function of migration rate ($m$),
            measured as the number of generations
            until the introduced population's mean phenotype is within 0.5 
            of the original lakes average phenotype. 
            Each point represents a single simulation, and
            the line shows the average of all points at each value of $m$.
        }
  		\label{fig:TimeToAdaptation}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
        \includegraphics[width=\linewidth]{plotlyPlots/NumFAA}
        \includegraphics[width=\linewidth]{matplotlibPlots/MPFAI}
  		\caption{
            \textbf{(A)}
            Distribution of the number of freshwater adapted alleles (green)
            and the average number of lakes each allele is present in (red)
            across the course of the simulation.
            \textbf{(B)}
            Distributions of mean percentage of freshwater adapted alleles (FAA) per individual throughout the simulation run, for each subpopulation.
		We count the total number of freshwater alleles for each individual before averaging them in each population and dividing by the total number of defined
		freshwater adapted alleles.
		Looking at total number of FAA per individual gives us an idea behind how many alleles underly a freshwater haplotype, 
		while the percentage tells us the variance of the haplotype}
		\label{fig:MPFAI}
	\end{center}
\end{figure}

@@

%FIGURES THAT SHOW THIS:
%- Phenotype Distribution
%GENERAL

@@

\begin{figure}
	\begin{center}
        \includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-3}
        \includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-4}
  		\caption{(Description and cleaning needed)
		}
  		\label{fig:Fst3}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{matplotlibPlots/Power_FP.png}
  		\caption{ 
		%SP - suppose you have an Fst Peak, how likely is it that that region is causal. 
		Statistical Power and False Positives as a function of $F_{st}$ threshold. 
		Statistical Power is the likelihood that a SNP will be predicted to have an effect on phenotype when there is an effect to be detected (?).
		False Positives give us the ratio of SNPs that effect phenotype to total SNPs greater than the $F_{st}$ threshold.
        TODO: x-axis label ($F_{ST}$).
		}
  		\label{fig:Power_FP}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{plotlyPlots/StandingGeneticVariation.png}
  		\caption{(PLACEHOLDER)}
		\label{fig:SGV}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{matplotlibPlots/MFAI.png}
  		\caption{Distributions of mean number of freshwater adapted alleles (FAA) per individual throughout the simulation run, for each subpopulation.
		We count the total number of freshwater alleles for each individual before averaging them in each population and dividing by the total number of defined
		freshwater adapted alleles.
		Looking at total number of FAA per individual gives us an idea behind how many alleles underly a freshwater haplotype, 
		}
  		\label{fig:MNFAI}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{matplotlibPlots/effectRegionCounts.png}
  		\caption{(PLACEHOLDER)}
		\label{fig:counts}
	\end{center}
\end{figure}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-5.png}
  		\caption{ (PLACEHOLDER)
		}
  		\label{fig:Fst1}
	\end{center}
\end{figure}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-2.png}
  		\caption{(PLACEHOLDER)
		}
  		\label{fig:Fst4}
	\end{center}
\end{figure}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-5.png}
  		\caption{ (PLACEHOLDER)
		}
  		\label{fig:phenotype_ts1}
	\end{center}
\end{figure}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-2.png}
  		\caption{(PLACEHOLDER)
		}
  		\label{fig:phenotype_ts4}
	\end{center}
\end{figure}

>>>>

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.8\linewidth]{matplotlibPlots/Fst_Adaptation.png}
  		\caption{Distributions of $F_{st}$  values between the three subpopulations throughout the simulations.
		On the left, $F_{st}$ was calculated only on neutral mutation frequencies. On the right, $F_{st}$ was calculated
		only on effect (Impact on phenotype) mutation frequencies. 
		Effect mutations are acted upon by selection as they have an affect on fitness where neutral mutations  }
  		\label{fig:Fst}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.8\linewidth]{matplotlibPlots/Adaptation_2_matplot.png}
  		\caption{Time to adaptation as a function of migration rate ($M$) parameter value. This is where we measure how many generation
		it takes for the introduced population's mean phenotype to come within 0.5 of the original lakes average phenotype. 
		Each point represents a simulation run at some value of $M$. 
		The yellow dashed line is the average of all points at each respective parameter value}
  		\label{fig:TimeToAdaptation}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{matplotlibPlots/MPFAI_2_matplot.png}
  		\caption{Distributions of mean percentage of freshwater adapted alleles (FAA) per individual throughout the simulation run, for each subpopulation.
		We count the total number of freshwater alleles for each individual before averaging them in each population and dividing by the total number of defined
		freshwater adapted alleles.
		Looking at total number of FAA per individual gives us an idea behind how many alleles underly a freshwater haplotype, 
		while the percentage tells us the variance of the haplotype}
		\label{fig:MPFAI}
	\end{center}
\end{figure}

@@

%FIGURES THAT SHOW THIS:
%- Phenotype Distribution
\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.6\linewidth]{matplotlibPlots/Pheno_2_matplot.png}
  		\caption{Distribution of mean phenotype throughout simulation runs at separate migration rate ($M$) parameter values, for each population.
		The dashed pink line (Pheno = +10) is the optimum phenotype any individual in the marine environment.
		In contrast the purple line at (Pheno = -10) represents the optimum for any individual in the freshwater environment. 
		All individuals at generation 0 (beginning of the simulation) 
		}
  		\label{fig:MeanPhenotype}
	\end{center}
\end{figure}

%GENERAL

@@

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{matplotlibPlots/0_25_power.png}
  		\caption{ 
		%SP - suppose you have an Fst Peak, how likely is it that that region is causal. 
		Statistical Power and False Positives as a function of $F_{st}$ threshold. 
		Statistical Power is the likelihood that a SNP will be predicted to have an effect on phenotype when there is an effect to be detected (?).
		False Positives give us the ratio of SNPs that effect phenotype to total SNPs greater than the $F_{st}$ threshold.
        TODO: x-axis label ($F_{ST}$).
		}
  		\label{fig:Power_FP}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{matplotlibPlots/MFAI_2_matplot.png}
  		\caption{Distributions of mean number of freshwater adapted alleles (FAA) per individual throughout the simulation run, for each subpopulation.
		We count the total number of freshwater alleles for each individual before averaging them in each population and dividing by the total number of defined
		freshwater adapted alleles.
		Looking at total number of FAA per individual gives us an idea behind how many alleles underly a freshwater haplotype, 
		}
  		\label{fig:MNFAI}
	\end{center}
\end{figure}
